Data Imputation as a Query Optimization

### 2016-12-07 paper/algorithm.tex
paper: a fluffy complexity section

\subsection{Complexity}

>>>>

\subsection{Complexity}
Our optimization algorithm builds off the approach taken by System R\cite{blasgen1981system}, therefore our algorithm still operates in exponential time. Indeed, 
note that if we remove our restriction on types of imputation($\delta_{min}, \mu_{min}, \mu_{max}$), and allow any arbitrary subset of attributes to be imputed,
then every single operator in the query plan has a number of imputations exponential in the number of dirty columns. Our restriction, instead, increases the number
of plans (in the worst case) at each operator by a factor of 3. Of course, this implies that in the worst case (where all dirty sets tracked are distinct throughout the query plan),
we explore a number of plans that further scales the number of plans in the original algorithm by an exponential factor.

However, we note that in all cases we have considered, this exponential blowup does not affect the practical performance of our optimizer.
